\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
3.3

%\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
%These axiom types are sometimes considered as basic axiom types in DL - using some suggestive notation such as
%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
%Such axioms, however, are just syntactic sugar - 
%all role characteristics can be expressed using the basic features of DL.
%
%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
%\begin{DL}
%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
%\end{DL}
%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
%
%%\begin{gcotable}
%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Complex Constraints}
	%\label{tab:irreflexive-object-properties-as-complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		%\end{tabular}
%\end{table}
%
%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
%
%%\begin{gcotable}
%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Simple Constraints}
	%\label{tab:irreflexive-object-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & authorOf & - & - & irreflexive & - \\
		%\end{tabular}
%\end{table}
The \emph{primary key properties (R-226)} constraint type is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
Books, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
which can be represented using the RDF-CV in form of a complex constraint consisting of two simple constraints (see Table \ref{tab:primary-key-properties-as-complex-constraints}).

@@

Constraints of the \emph{irreflexive object properties (R-60)} constraint type ensure that no individual is connected by a given object property to itself \cite{Kroetzsch2012}. With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves. When represented using the RDF-CV, the complex constraint aggregates three simple constraints - one property and two class constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).

@@

When using the irreflexive object property constraint in terms of syntactic sugar, 
the complex constraint can be expressed more concisely in form of a simple property constraint with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):

>>>>

%\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
%These axiom types are sometimes considered as basic axiom types in DL - using some suggestive notation such as
%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
%Such axioms, however, are just syntactic sugar - 
%all role characteristics can be expressed using the basic features of DL.
%
%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
%\begin{DL}
%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
%\end{DL}
%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
%
%%\begin{gcotable}
%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Complex Constraints}
	%\label{tab:irreflexive-object-properties-as-complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		%\end{tabular}
%\end{table}
%
%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
%
%%\begin{gcotable}
%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Simple Constraints}
	%\label{tab:irreflexive-object-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & authorOf & - & - & irreflexive & - \\
		%\end{tabular}
%\end{table}
The \emph{primary key properties (R-226)} constraint type is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
Books, e.g., are uniquely identified by their ISBN, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
which can be represented using the RDF-CV in form of a complex constraint consisting of two simple constraints (see Table \ref{tab:primary-key-properties-as-complex-constraints}).

@@

Constraints of the \emph{irreflexive object properties (R-60)} constraint type ensure that no individual is connected by a given object property to itself \cite{Kroetzsch2012}. With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves. When represented using the RDF-CV, the complex constraint aggregates three simple constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).

@@

When using the \emph{irreflexive object property} constraint in terms of syntactic sugar, 
the complex constraint can be expressed more concisely in form of a simple property constraint with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
